% -*- compile-command: "latexmk -pdf document.tex" -*-
\documentclass[12pt]{article}

\author{Sam Price}
\title{Reflection 11}
\date{November 19, 2024}

\newif\ifprinted%
%\printedtrue%
\input{preamble}

\begin{document}

\maketitle

This week was a helpful one in all the math I did.
First, let's talk about the things I concretely got done.
I tidied up the cross-line non-homeomorphism quite nicely by realizing bijectivity disallows specifically disjoint unions of open sets being one connected open set.
Obviously, this had to be true almost by the definition of connectedness, but was good to finalize.
I also finished up the $\GL,\SL$ manifold proofs.
You said earlier today that the reasoning behind $D\det$ being nonsingular was less complete/coherent than it should be,
I'll include what I believe is more concise and understandable proof at the bottom.

This week in 464 has been quite nice. Today felt far better than it has for a while now, but seeing pieces fall into place feels satisfying now.
Differential forms feel more or less intuitive as we go along, and the algebra is great when almost everything disappears in one fell swoop.

I have my work cut out for me for the next week or two -\ definitely going to get busy while I'm away from campus.
The two big parts are the capstone theorem that I'll show off (``present'') during finals as well as the exercises in order to get all the math-only stuff done.
I don't think the capstone will take \emph{all} the time though, since I have many resources to look at as well as \textbf{plenty} of time to work through my proof(s)
meticulously.

\underline{Determinant argument}: Let $J = D\det$ for a fixed $n \times n$ matrix case.
Clearly, $\rank J = 0$ iff every entry is zero, but we will concern ourselves with only the first $n$ entries.
The entry in $J$ for each of the $a_{1,n}$ is precisely $\pars{-1}^{n + 1}m_{1,n}$.
If all such entries are zero, this is a problem, as we have
\[ \det A = \sum_{i = 1}^{n}\pars{-1}^{n + 1}a_{1,n}m_{1,n} = \sum_{i = 1}^{n}a_{1,n} \cdot 0 = 0 \]
which is a contradiction as we assume first $A \in \GL_{n}$ and so has nonzero determinant.

\end{document}
