% -*- compile-command: "latexmk -pdf document.tex" -*-
\documentclass[12pt]{article}

\author{Sam Price}
\title{Reflection 12}

\newif\ifprinted%
%\printedtrue%
\input{preamble}

\begin{document}

\maketitle

This week has been substantial in terms of progress, but perhaps not in terms of \emph{finishing} things.
Sometimes that is a good thing, although I'd prefer the latter for obvious reasons.

Let's begin with progression:
I've done some nice progress on the exercise that shows linearity,
composition and wedge-distribution of the pullback.
I think what I need to do is review all the pullback/pushforward content so that it feels smoother
when piecing parts together.

I've also started playing more with the specified 2-form to show that it is closed but not exact.
I'll put more pen-to-paper on that later today, but I feel good about that.

Another thing I'll get on is figuring out the one step of orientability we couldn't quite piece together in class.
I also want to get an explanation together for why the induced orientation flips depending on dimension, since
I feel it will also build intuition for Stokes' and related ideas.

Somewhere in the middle of priorities is to get a large chunk, if not all, of the capstone theorem done.
Looking at Tao's proof (and greater book as a whole) I am \emph{very} glad we don't use his notation.
Simply using $f'$ for the Jacobian is way more confusing that simply the choice of $J$ versus $D$ prefixing.
That definitely took some time to get used to.

\underline{Questions \& Muddled Points}:
When I read the (correct) pullback page on Wikipedia, it starts from taking $\phi$ as a general
smooth map between manifolds.
Is our definition for charts and the like just a special case of this since $\RR[k]$ is a manifold,
and we don't exactly have time for more nuance? I'd guess so, but since it's only a guess I figure asking is best.

The last order of business is to review all the math stuff, since Finals Week is upon us.
I am partly relieved because my GOODNESS what a semester for so many reasons, but at the same time I realize
I should have done a lot more both for this class and otherwise. Research updates to come as well!

Unrelated, but thoughts on Ding flagging in the WCC?\@ That is crazy to see happen.
I hope this \emph{isn't} a repeat of Carlsen-Nepo game 6 in that Ding just crashes out and falls apart
in the games after this. If he doesn't fall back an HOUR on time while Gukesh is still in prep then he has a chance.
It would be cool to see Gukesh be the youngest WC ever though, by a whole four years.

\end{document}
